Evaluation of performances

### 2019-08-31 analysis/eval-performance.Rmd
wflow_publish(knitr_in("analysis/eval-performance.Rmd"), view = FALSE, verbose = TRUE)

```{r eval-performance-3}
results_aggr <- getBMRAggrPerformances(bm_aggregated, as.df = TRUE) %>%
  mutate(task.id = recode_factor(task.id,
    `defoliation-all-plots-HR` = "HR",
    `defoliation-all-plots-VI` = "VI",
    `defoliation-all-plots-NRI` = "NRI",
    `defoliation-all-plots-HR-NRI` = "HR-NRI",
    `defoliation-all-plots-HR-VI` = "HR-VI",
    `defoliation-all-plots-HR-NRI-VI` = "HR-NRI-VI",
  )) %>%
  tidyr::separate(learner.id, c("learner_group"),
    remove = FALSE,
    sep = " "
  ) %>%
  group_by(learner_group, task.id) %>%
  summarise(best = min(rmse.test.rmse))

results_aggr %>%
  ggplot(aes(x = best, y = task.id)) +
  geom_point(aes(color = learner_group, size = 1.7)) +
  scale_color_nejm() +
  labs(x = "RMSE", y = "Task", color = "Learner") +
  guides(size = FALSE) +
  scale_x_continuous(limits = c(1.8, 4)) +
  geom_label_repel(
    label = round(results_aggr$best, 3),
    size = 3, nudge_y = 0.3
  ) +
  theme_pubr()
```

>>>>

```{r performance-results, warning=FALSE, dev = c("png", "pdf")}
results_aggr <- getBMRAggrPerformances(bm_aggregated, as.df = TRUE) %>%
  mutate(task.id = recode_factor(task.id,
    `defoliation-all-plots-HR` = "HR",
    `defoliation-all-plots-VI` = "VI",
    `defoliation-all-plots-NRI` = "NRI",
    `defoliation-all-plots-HR-NRI` = "HR-NRI",
    `defoliation-all-plots-HR-VI` = "HR-VI",
    `defoliation-all-plots-HR-NRI-VI` = "HR-NRI-VI",
  )) %>%
  tidyr::separate(learner.id, c("learner_group", "filter"),
    remove = FALSE,
    sep = " "
  ) %>%
  mutate(filter = replace(filter, is.na(filter), "NF")) %>%
  mutate(learner_group = recode_factor(learner_group, `XG` = "XGBOOST")) %>% 
  group_by(learner_group, task.id) %>%
  # get the best performance per learner and task
  # this is better than summarise() because we can keep additional columns
  # in constrast to summariuse which only keeps the grouping columns and the
  # summarised one
  slice(which.min(rmse.test.rmse))

results_aggr %>%
  ggplot(aes(x = rmse.test.rmse, y = task.id)) +
  geom_point(aes(color = learner_group), size = 2.5) +
  scale_color_nejm(breaks = sort(levels(results_aggr$learner_group))) +
  labs(x = "RMSE log(x)", y = "Task", color = "Learner") +
  guides(size = FALSE) +
  scale_x_continuous(limits = c(30, 70)) +
  # geom_label_repel(
  #   label = round(results_aggr$rmse.test.rmse, 3),
  #   size = 3, nudge_y = 0.3
  # ) +
  geom_label_repel(
    label = paste(results_aggr$filter,",",round(results_aggr$rmse.test.rmse, 3)),
    size = 2.8
  ) +
  theme_pubr()
```
